---
title: "R/Shiny Review- Data Challenge 2 Phase 2"
author: "Sumit Dhar"
date: "10/18/2020"
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objective

* Consider this as a 101 'nuts & bolts' session
* Build Shiny Apps based on R/Shiny 
  Understand the various pieces of the standard template
* Customize Reactions
  We cover more details in the afternoon session where we cover interactiosn between LpSolve/ LpSolveAPI and Shiny
* Provide quick inputs to build Optimization App/ Simulator in R Shiny  

## 1. The Basic Template  

Shortest viable R/Shiny App...
```{r echo= TRUE}
# Load Shiny
library(shiny)
# Create the UI with HTML function
ui <- fluidPage(
  # Input() Functions,
  # Output() Functions
)
#Create a custom function to create server
server <- function(input, output, session){}  
shinyApp(ui= ui, server= server)
```

## 2. Inputs: With an Input() Function  

```{r results='asis'}
library(shiny)
# Create the UI with HTML function
sliderInput(inputId = 'num', label= 'choose a number', value=25, min=1, max=100)
```

  
## 3. Input Functions  
Couple of examples. For more ideas: https://shiny.rstudio.com/tutorial/written-tutorial/lesson3/

```{r echo=TRUE}
library(shiny)
# Create the UI with HTML function
ui <- fluidPage(h3("Slider"),
  sliderInput(inputId = 'num', label= 'choose a number', value=25, min=1, max=100),
  h3(""),
  selectInput("select", h3("Select box"), 
                       choices = list("Choice 1" = 1, "Choice 2" = 2,
                                      "Choice 3" = 3), selected = 1)
  # Drop Down
  # Binary Select
  # 
)
#Create a custom function to create server
server <- function(input, output, session){}
shinyApp(ui= ui, server= server)
```

##  4. Output Functions  
Output() adds space in the ui for a R object. You need to build the object
Reference to Output Functions: https://shiny.rstudio.com/reference/shiny/1.0.5/

```{r echo=TRUE}
library(shiny)
# Create the UI with HTML function
ui <- fluidPage(h3("Slider"),
  sliderInput(inputId = 'num', label= 'choose a number', value=25, min=1, max=100),
  plotOutput("hist")
)
#Create a custom function to create server
server <- function(input, output, session){}
shinyApp(ui= ui, server= server)
```

##  5. 3 rules of server functions  

You tell the server function how to assemble inputs & Outputs  
Output needs to be built in the server section    

1. Save Objects to display to output$  
2. Build objects to display with render()  
3. Reference input values with input$  
  
## 6. render() function to build objects to display  

Builds a reactive output to display on the UI  

```{r echo=TRUE}
library(shiny)
# Create the UI with HTML function
ui <- fluidPage(h3("Slider"),
  sliderInput(inputId = 'num', label= 'choose a number', value=25, min=1, max=100),
  plotOutput("hist")
)
#Create a custom function to create server
server <- function(input, output, session){
  output$hist <- renderPlot({
    title <- '100 random normal values'
    hist(rnorm(100), main= title)
  })
}
shinyApp(ui= ui, server= server)
```
  

## 7. Basics of Reactivity  

Reactivity automatically occurs when a input is used to manipulate the output

```{r echo=TRUE}
library(shiny)
# Create the UI with HTML function
ui <- fluidPage(h3("Slider"),
  sliderInput(inputId = 'num', label= 'choose a number', value=25, min=1, max=100),
  plotOutput("hist")
)
#Create a custom function to create server
server <- function(input, output, session){
  output$hist <- renderPlot({
    title <- paste0(input$num, ' random normal values')
    hist(rnorm(input$num), main= title)
  })
}
shinyApp(ui= ui, server= server)
```

## 8. Basics of Reactivity  

Reactivity automatically occurs when a input is used to manipulate the output

```{r echo=TRUE}
library(shiny)
# Create the UI with HTML function
ui <- fluidPage(h3("Slider"),
  sliderInput(inputId = 'num', label= 'choose a number', value=25, min=1, max=100),
  plotOutput("hist")
)
#Create a custom function to create server
server <- function(input, output, session){
  output$hist <- renderPlot({
    title <- paste0(input$num, ' random normal values')
    hist(rnorm(input$num), main= title)
  })
}
shinyApp(ui= ui, server= server)
```
