---
title: "R/Shiny Review- Data Challenge 2 Phase 2"
author: "Sumit Dhar"
date: "10/16/2020"
output:
  slidy_presentation: default
  toc: true
  ioslides_presentation: default
  sansfont: Calibri Light
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# 9. reactive() in action  

1. You can call reactive() expression as a function
2. Reactive expressions **cache** their values and store recent value until invalidated

```{r echo=TRUE}
library(shiny)
# Create the UI with HTML function
ui <- fluidPage(h3("Slider"),
  sliderInput(inputId = 'num', label= 'choose a number', value=25, min=1, max=100),
  plotOutput("hist"),
  verbatimTextOutput("stats")
)
#Create a custom function to create server
server <- function(input, output, session){
  data <- reactive(rnorm(input$num))
  output$hist <- renderPlot({
    title <- paste0(input$num, ' random normal values')
    hist(data(), main= title)
  })
  output$stats <- renderPrint({summary(data())})
}
shinyApp(ui= ui, server= server)
```

# 10. eventReactive()  
Reactive expression that responds to specific events  

```{r echo=TRUE}
library(shiny)
# Create the UI with HTML function
ui <- fluidPage(h3("Slider"),
  sliderInput(inputId = 'num', label= 'choose a number', value=25, min=1, max=100),
  actionButton(inputId = 'Go', label= 'Update'),
  plotOutput("hist"),
  verbatimTextOutput("stats")
)
#Create a custom function to create server
server <- function(input, output, session){
 data <- eventReactive(input$Go, {
   rnorm(input$num)
 })
 output$hist <- renderPlot({
   hist(rnorm(data()))
 })
 output$stats <- renderPrint({summary(data())})
}
shinyApp(ui= ui, server= server)
```


## Things to remember  
- Code Outside server function runs once per R session
- Code inside server function will be run once per end user
- Code inside a reactive function will be run once per reaction



